In order to realise this project, the activities need to be devised. describing the end-product in precise terms will make it easier to devise those tasks. These activities are: 

\begin{itemize}
	\setlength\itemsep{-0.3em}
	\item Planning
	\item Research
	\item Designing
	\item Testing
	\item Writing documentation
	\item Budget tracking
\end{itemize}


	\section{Planning}
	
The planning is one of the most important stages within the project activities, this gives you the broad overview over the whole project and what it is going to look like. In order to determine the activities, progress, costs, duration and delay of a project, a planning is of the essence. 
The planning will be divided into two separate parts:

\begin{itemize}
	\setlength\itemsep{-0.3em}
	\item Global planning
	\item Personal (weekly or daily) planning
\end{itemize}
\noindent
The global planning will be made in Gantt-chart style. The personal planning is freer of choice depended on the team member itself. \\
	
	
	\section{Research}
	
In chapter 2 Project result the research questions are described. Those questions need to be answered before specifying the things that are needed to start working on this project. This phase is especially important because of its responsibility that it carries in future development of the project. The better the research is done, the less wrongly things will be executed in the future stage of the project, which will save time. 
The research questions will be separated in two categories: 

\begin{itemize}
	\setlength\itemsep{-0.3em}
	\item The research questions that will be split into the team members that have the interest in the specific subject based on their PDP.
	\item The research questions that needed to be discussed in a group matter, so everyone is on par with the research and knowledge.\\
\end{itemize}



	\section{Designing}
	
During this stage most of the research will have been completed and the tasks will be divided into the team members. Depended on the PDP and the preferred modules the team members will work either together or alone on a module. While designing the other team members will be updated in the weekly meetings.  \\
	
	\section{Testing}
	
After the design phase the modules will be put together and will be tested based on the test report. \\
	
	
	\section{Writing Documentation}
	
If all the necessary requirements (user and functional) are fulfilled and testing is done, the evidence will be put in the final report. \\
	
	\section{Budget tracking}
	
Fontys has provided us with a budget of €300, - for the completion of this project. The most expensive parts expected will be the processor, the ADC’s and the DAC’s. \\

	\section{Activities}

\begin{itemize}
	\setlength\itemsep{-0.3em}
	\item Reporting
	\begin{itemize}
		\setlength\itemsep{-0.3em}
		\item Creating SRD
		\item Creating SDD
		\item Creating MDD
		\item Creating final report
	\end{itemize}
	\item Researching research questions
	\begin{itemize}
		\setlength\itemsep{-0.3em}
		\item Creating research document
	\end{itemize}
	\item Designing
	\begin{itemize}
		\setlength\itemsep{-0.3em}
		\item Design firmware:
		\begin{itemize}
			\setlength\itemsep{-0.3em}
			\item Design input MUX
			\item Design sampler
			\item Design USB decoder
			\item Design output MUX
			\item Design signal processor:
			\begin{itemize}
				\setlength\itemsep{-0.3em}
				\item Design effect manager
				\item Design/model/simulate effects
				\item Design/model/simulate filters
			\end{itemize}
			\item Design controller
		\end{itemize}
		\item Design hardware:
		\begin{itemize}
			\setlength\itemsep{-0.3em}
			\item Design input selector
			\item Design anti-aliasing filters
			\item Design output filter
			\item Design buffer
			\item Design XLR balanced-to-unbalanced converter
			\item Design XLR unbalanced-to-balanced converter
			\item Design processor core
			\item Design local power supplies
			\item Design housing
		\end{itemize}
		\item Design user interface
	\end{itemize}
	\item Realisation
	\begin{itemize}
		\setlength\itemsep{-0.3em}
		\item Program firmware:
		\begin{itemize}
			\setlength\itemsep{-0.3em}
			\item Program ADC and DAC interface
			\item Program sampler
			\item Program USB decoder
			\item Program MUX
			\item Program signal processor:
			\begin{itemize}
				\setlength\itemsep{-0.3em}
				\item Program effect manager
				\item Program filters
				\item Program effects
			\end{itemize}
			\item Program controller 
		\end{itemize}
		\item Create hardware:
		\begin{itemize}
			\setlength\itemsep{-0.3em}
			\item Create housing
			\item Realize PCB
		\end{itemize}
		\item Program user interface 
	\end{itemize}
	\item Testing
	\begin{itemize}
		\setlength\itemsep{-0.3em}
		\item Verify firmware:
		\begin{itemize}
			\setlength\itemsep{-0.3em}
			\item Verify ADC and DAC interface	
			\item Verify Sampler
			\item Verify USB decoder
			\item Verify MUX
			\item Verify signal processor:
			\begin{itemize}
				\setlength\itemsep{-0.3em}
				\item Verify effects manager
				\item Verify filters
				\item Verify effects
			\end{itemize}
			\item Verify controller
		\end{itemize}
		\item Verify hardware
		\item Verify user interface
	\end{itemize}
\end{itemize} 


	