The goal of this project is to research how to make an audio-DSP. This raises the main research question: \textbf{“How to design an audio-DSP?”}. In the process of researching this an actual audio-DSP will be developed. From the main research question the following sub-research questions are derived:
\begin{itemize} %THIS IS TO MAKE LISTS
	\setlength\itemsep{-0.3em} %MAKES THE GAP SMALLER BETWEEN 2 ITEMS
	\item What is the best method for creating digital filters?
	\item What is the best method for creating digital effects?
	\item What is the most suitable anti-aliasing filter?
	\item What is the optimal needed roll-off for the anti-aliasing filter for a given bandwidth such that the noise can be negligible?
	\item What is the minimum sample frequency needed to capture the desired frequency spectrum?
	\item What is the minimum frequency range to be sampled to achieve sufficient detailed audio?
	\item What is the lowest allowable noise for decent audio?
	\item What analog to digital converter (ADC) resolution is needed such that the quantization error and noise level are on par?
	\item What ADC and digital to analog converter (DAC) architecture is most suitable for this application?
	\item What kind of processor is most suitable for this application?
	\item What is the permittable jitter for accurate audio?
	\item What is the maximum allowable ripple on the reference voltage for the ADC and DAC?
	\item How much RAM does the system need?
	\item How much flash does the system need?
	\item What power supply topology is best suited for each part of the system? \\
\end{itemize}

\noindent
The project is conducted during the minor BeCreative at Fontys. This minor takes 20 weeks and allows the students to have a budget of €300,-. Thus after 20 weeks starting from 6-2-2023 an audio-DSP will be delivered within a budget of €300,-.
\par
\noindent
The audio system has some requirements to specify the final result. These requirements are derived with the “MoSCoW” method. It must be noted that the following requirements will be confirmed by the research that will be conducted.

	\newpage
	\section{Requirements}
	\begin{longtable}{|c|p{10cm}|c|c|}
		\hline
		\textbf{ID} & \textbf{Requirement} & \textbf{Priority} & \textbf{Status}\\ \hline 
		\textbf{U1} & \textbf{Inputs:} \newline
		•Two RCA audio inputs which work on a line level of 4dBu(±1,74V)\newline
		•Two 6,35mm TRS plug audio inputs which work on a line level of 4dBu(±1,74V)\newline
		•Two XLR audio inputs which work on a line level of 22dBu(±9,75)\newline
		•USB type B audio input & Must & Proposed\\ \hline

		\textbf{U2} & \textbf{Outputs:} \newline
		•Two RCA audio outputs which work on a line level of 4dBu(±1,74V)\newline
		•Two 6,35mm TRS plug audio outputs which work on a line level of 4dBu(±1,74V)\newline
		•Four XLR signal outputs which work on a line level of 22dBu(±9,75)
		 & Must & Proposed\\ \hline

		\textbf{U3} &The system should have a bandwidth (±3 dB) of at least 20 Hz up and till 20 kHz without any filters applied. 	& Must   & Proposed\\ \hline
		\textbf{U4} &The system has an Audio sample rate of at least 44.1 kHz 														& Must   & Proposed\\ \hline
		\textbf{U5} &The ADC and DAC resolution is at least 16-bit 																	& Must   & Proposed\\ \hline
		\textbf{U6} &The system has a propagation delay of less than 100ms without any filters applied 								& Must   & Proposed\\ \hline
		\textbf{U7} &User can select what input will be used via a user interface													& Must   & Proposed\\ \hline
		\textbf{U8} &User can select up to 4 effects to active on one channel at the same time 										& Must   & Proposed\\ \hline
		\textbf{U9} &User can configure each effect 																				& Must   & Proposed\\ \hline
		\textbf{U10} &The system must work stand alone and be configurable via a basic graphical user interface 					& Must   & Proposed\\ \hline
		\textbf{U11} &Effects are configurable per output channel, at least four different sound effects should be able to be applied to each signal output signal at the same time: \newline
		\begin{itemize}
			\setlength\itemsep{-0.4em}
			\item Distortion
			\item Reverb
			\item Gain
			\item Equalizer
			\item Delay
		\end{itemize}																												& Must 	 & Proposed\\ \hline
		\textbf{U12}  &The system should have a bandwidth (±1 dB) of at least 20 Hz up and till 20 kHz without any filters applied 	& Should & Proposed\\ \hline
		\textbf{U13}  &Audio sample rate of at least 96 kHz 																		& Should & Proposed\\ \hline
		\textbf{U14} & The ADC and DAC resolution is at least 24-bit. 																& Should & Proposed\\ \hline
		\textbf{U15} & Six XLR signal outputs work on a line level of 22 dBu (±9,75 V) 												& Should & Proposed\\ \hline
		\textbf{U16} & User can select up to 10 effects to be active in one channel at the same time. 								& Should & Proposed\\ \hline
		\textbf{U17} & Low enough jitter to not influence the audio quality too much 												& Should & Proposed\\ \hline
		\textbf{U18} & Local power supplies for different parts of the system 														& Should & Proposed\\ \hline
		\textbf{U19} & Low enough jitter to not influence the audio quality too much 												& Should & Proposed\\ \hline
		\textbf{U20} & Effects:\newline
		\begin{itemize}
			\setlength\itemsep{-0.3em}
			\item Phaser
			\item Tremelo
			\item Flanger
			\item Fuzz
			\item Overdrive
			\item Chorus
			\item Compressor
			\item Wah
			\item Looper
			\item Wow and flutter
			\item Modulator
			\item Echo
			\item Fade in
		\end{itemize}																												& Should & Proposed\\ \hline
		\textbf{U21} & Audio sample rate of at least 192 kHz 																		& Could  & Proposed\\ \hline
		\textbf{U22} & Touch screen user interface 																					& Could  & Proposed\\ \hline
		\textbf{U23} & Self-made mains power supply  																				& Won't  & Proposed\\ \hline
	\end{longtable}